### 2019-10-25 paper/abstract.tex
After Tikhomirov's and Matthew's comments

\begin{abstract}
Liquid-fueled \gls{MSR} systems represent advances in safety, economics, sustainability, and proliferation-resistance. The \gls{MSR} has been designed to operate in Th/$^{233}$U fuel cycle with $^{233}$U used as startup fissile material. Since $^{233}$U does not exist in nature, it is required to examine other available fissile materials. This work investigated the fuel cycle and neutronics performance of the \gls{SD-TMSR} with different fissile material loadings at startup: \gls{LEU} (19.79\%), Pu mixed with \gls{LEU} (19.79\%), Pu reactor-grade (a mixture of plutonium isotopes chemically extracted from \gls{PWR} \gls{SNF} with $33$ $GWd/tHM$ burnup), \gls{TRU} from \gls{LWR} \gls{SNF}, and $^{233}$U.
The \gls{MSR} burnup routine provided by SERPENT-2 has been used to simulate the online reprocessing and refueling in the \gls{SD-TMSR}. The effective multiplication factor, fuel salt composition evolution and net production of $^{233}$U have been studied in the present work. Additionally, the neutron spectrum shift during the reactor operation was calculated. The results showed that the continuous flow of Pu reactor-grade helps transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ years) compared to $26$ years for $^{233}$U startup fuel. Finally, using \gls{TRU} as initial fissile materials offers the possibility of operating the SD-TMSR for an extended period of time ($\approx$ $40$ years) without any external feed of $^{233}$U.
\end{abstract}

>>>>

\begin{abstract}
Liquid-fueled \gls{MSR} systems represent advances in safety, economics, sustainability, and proliferation resistance. The \gls{MSR} has been designed to operate in Th/$^{233}$U fuel cycle with $^{233}$U used as startup fissile material. Since $^{233}$U does not exist in nature, We must examine other available fissile materials. This work investigates the fuel cycle and neutronics performance of the \gls{SD-TMSR} with different fissile material loadings at startup: \gls{LEU} (19.79\%), Pu mixed with \gls{LEU} (19.79\%), reactor-grade Pu (a mixture of Pu isotopes chemically extracted from \gls{PWR} \gls{SNF} with $33$ $GWd/tHM$ burnup), \gls{TRU} from \gls{LWR} \gls{SNF}, and $^{233}$U.
The \gls{MSR} burnup routine provided by SERPENT-2 is used to simulate the online reprocessing and refueling in the \gls{SD-TMSR}. The effective multiplication factor, fuel salt composition evolution and net production of $^{233}$U are studied in the present work. Additionally, the neutron spectrum shift during the reactor operation is calculated. The results show that the continuous flow of reactor-grade Pu helps transition to the thorium fuel cycle within a relatively short time ($\approx$ $4.5$ years) compared to $26$ years for $^{233}$U startup fuel. Finally, using \gls{TRU} as initial fissile materials offers the possibility of operating the SD-TMSR for an extended period of time ($\approx$ $40$ years) without any external feed of $^{233}$U.
\end{abstract}

### 2019-10-25 paper/conclusion.tex
After Tikhomirov's and Matthew's comments

Five different types of initial fissile loadings have been studied for 
transitioning to the thorium fuel cycle in the \gls{SD-TMSR}. We 
adopted two different feed mechanisms: thorium feed mechanism and non-thorium 
feed mechanism. Lifetime-long depletion for the whole-core SD-TMSR model was 
performed with Pu reactor-grade, TRU, and $^{233}$U as initial fissile 
materials. Additionally, the dynamics of the effective multiplication factor 
$k_{eff}$, major isotopes mass, neutron energy spectrum, and essential safety 
parameters have been investigated.

Results demonstrated that continuous flow of Pu reactor-grade allows the 
transition to the thorium fuel cycle in a relatively short time ($\approx$ 
$4.5$ years) compared to $26$ years for Th/$^{233}$U startup fuel. 
Meanwhile, using \gls{TRU} as initial fissile materials shows the possibility 
of operating the SD-TMSR for an extended time ($\approx$ $40$ years) 
without any external feed of $^{233}$U. Notably, the Pu molar fraction (mole\%) in 
fuel salt was calculated and found to be below the solubility limit.

Additionally, the neutron energy spectrum shift during the reactor operation 
for the Pu and TRU cases is different from the $^{233}$U fueling scenario. 
Indeed, the spectrum hardening for $^{233}$U initial fissile isotope during 
operation, but softening for the Pu and TRU cases. Notably, the most 
significant neutron energy spectrum shift was obtained for reactor-grade Pu 
startup loading.

We compared the operational and safety parameters of the \gls{SD-TMSR} for all 
three startup fuels at both initial and equilibrium states. The total 
temperature coefficient of reactivity is negative and relatively large in all 
cases. For TRU case, the coefficient remained almost constant during 
operation: $-4.79\pm0.12$ $pcm/K$ and $-4.76\pm0.11$ $pcm/K$ for the initial 
and equilibrium states, respectively. For reactor-grade Pu, the coefficient 
absolute value decreased from $-6.54\pm0.16$ $pcm/K$ to $-4.79\pm0.12$ during 
60 years of operation. Finally, the six factors evolution during the operation 
were calculated for all three cases, and these parameters can be used to 
design the reactivity control system of the \gls{SD-TMSR}.

\section{Future work}
The authors intend to verify obtained results using another tool: batch-wise 
code SaltProc \cite{rykhlevskii_arfc/saltproc_2018,rykhlevskii_milestone_2019}.
Moreover, in further simulations, we intend to take into account the delayed 
neutron precursor drift. The \gls{SD-TMSR} reactivity control system has not 
been introduced in the literature yet. Thus, the control rods design and 
configuration might be suggested in the nearest future.

Lastly, an additional area to explore is the accident safety analysis which 
requires high-fidelity multi-physics model of the \gls{SD-TMSR} with the 
coupled neutronics/thermal-hydraulics software, Moltres 
\cite{lindsay_introduction_2018}. The full-core SERPENT-2 model of the 
\gls{SD-TMSR} and equilibrium fuel salt compositions, obtained in this work, 
would be employed to generate problem-oriented nuclear data libraries for 
Moltres. The ultimate goal of this effort is to develop a 
fast-running computational model for studying the dynamics behavior of generic 
\glspl{MSR}, performing safety analysis for different accident scenarios and 
optimizing design of various reactor concepts.

>>>>

Five different types of initial fissile loadings have been studied for 
transitioning to the thorium fuel cycle in the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR). We 
adopted two different feed mechanisms: thorium feed mechanism and non-thorium 
feed mechanism. Lifetime-long depletion for the whole-core SD-TMSR model was 
performed with reactor-grade Pu, TRU, and $^{233}$U as initial fissile 
materials. Additionally, the dynamics of the effective multiplication factor 
$k_{eff}$, major isotopes mass, neutron energy spectrum, and essential safety 
parameters have been investigated.

Results demonstrate that continuous flow of reactor-grade Pu allows the 
transition to the thorium fuel cycle in a relatively short time ($\approx$ 
$4.5$ years) compared to $26$ years for Th/$^{233}$U startup fuel. 
Meanwhile, using \gls{TRU} as initial fissile materials shows the possibility 
of operating the SD-TMSR for an extended time ($\approx$ $40$ years) 
without any external feed of $^{233}$U. Notably, the Pu molar fraction (mole\%) in 
fuel salt was calculated and found to be below the solubility limit.

The neutron energy spectrum shift during the reactor operation 
for the Pu and TRU cases is different from the $^{233}$U fueling scenario. 
The spectrum hardens for the $^{233}$U initial fissile isotope during 
operation, but softens for the Pu and TRU cases. Notably, the most 
significant neutron energy spectrum shift was obtained for reactor-grade Pu 
startup loading.

We compared the operational and safety parameters of the \gls{SD-TMSR} for all 
three startup fuels at both initial and equilibrium states. The total 
temperature coefficient of reactivity is negative and relatively large in all 
cases. For the TRU case, the coefficient remained almost constant during 
operation: $-4.79\pm0.12$ $pcm/K$ and $-4.76\pm0.11$ $pcm/K$ for the initial 
and equilibrium states, respectively. For reactor-grade Pu, the coefficient 
absolute value decreased from $-6.54\pm0.16$ $pcm/K$ to $-4.79\pm0.12$ during 
60 years of operation. Finally, the six factors evolution during the operation 
were calculated for all three cases, and these parameters can be used to 
design the reactivity control system of the \gls{SD-TMSR}.

\section{Future work}
The authors intend to verify obtained results using another tool: batch-wise 
code SaltProc \cite{rykhlevskii_arfc/saltproc_2018,rykhlevskii_milestone_2019}.
In further simulations, we intend to take into account the delayed 
neutron precursor drift. The \gls{SD-TMSR} reactivity control system has not 
been introduced in the literature yet. Thus, the control rods design and 
configuration might be suggested in the nearest future.

An additional area to explore is the accident safety analysis which 
requires high-fidelity multi-physics model of the \gls{SD-TMSR} with the 
coupled neutronics/thermal-hydraulics software, Moltres 
\cite{lindsay_introduction_2018}. The full-core SERPENT-2 model of the 
\gls{SD-TMSR} and equilibrium fuel salt compositions, obtained in this work, 
would be employed to generate problem-oriented nuclear data libraries for 
Moltres. The ultimate goal of this effort is to develop a 
fast-running computational model for studying the dynamics behavior of generic 
\glspl{MSR}, performing safety analysis for different accident scenarios and 
optimizing design of various reactor concepts.
